---
title: "Example Analysis"
author: "Jesper Fischer Ehmsen"
date: '2023-01-05'
output:
  html_document: default
---


### **importing libraries**
```{r message=FALSE}
pacman::p_load(tidyverse,ggdist,psycho,caret,patchwork, gt, cowplot, grid,reticulate, here)
np <- import("numpy")
```


### **Reading in the data, here the working diectory has be where the exmaple scripts are located**
```{r message=FALSE}
#This line reads in a subject result file:
df = read_csv("https://raw.githubusercontent.com/LegrandNico/Cardioception/master/docs/source/examples/templates/data/HRD/HRD_final.txt")

#These next lines read in the psi posterior distributions for each modality. 
#These will be saved with names depending on your conditions, so modify as needed. 
interoPost = np$load(here("docs","source","examples","templates","data","HRD","Intero_posterior.npy"))

exteroPost = np$load(here("docs","source","examples","templates","data","HRD","Extero_posterior.npy"))
```


### **Making an analysis on one participant**
#### **first loading in the functions**

```{r message=FALSE, results='hide',warning=FALSE}
#loading the functions to do the analysis:

source(here("docs","source","examples","R","src","firstlevelanalysis.R"))
```

#### This next function takes the raw data .txt file plus the posterior distributions for each staircase condition (e.g., extero vs intero).
#### If the numpy arrays (.npy) are not provided the function won't be able to produce the staircase plot.


#### **Arguments:**
#### df is the raw data frame, interoPost and exteroPost are the posterior distrubtions for each condition (if applicable). bayesian is a boolean flag, if set to TRUE, it'll run posthoc Bayesian threshold analysis, FALSE means to skip it. Note that to run this Bayesian analysis you'll need to install cmdstan and rstan. And to specify the stan model to run on the data see the exmaple_analysis_bayesian to do this note that the function drops NAs from the critical columns by default!


```{r message=FALSE, results='hide',warning=FALSE}
results = single_sub_analysis(df, interoPost = interoPost, exteroPost = exteroPost, bayesian = F, model = NA, out = here::here("docs","source","examples","R"))

```

### Note that these analyses can also be run with only one "Modality", important is that either the interopost or exteropost then gets set to NA

### **Results**

#### The returned list contains all individual subplots from the subject level analysis, and one (two) composite plots (two if bayesian = TRUE) Which are saved in the /results_sub directory. You can use these to generate individual plots, e.g. For example, the staircase plots:
```{r}
results$staircase_plot
```

#### Composite results plots are stored here
```{r,warning=FALSE, fig.height=10,fig.width=16}
results$concatenated_plot
```

#### all the invidual plots seen can be accessed in the results list by either calling the different indicies (e.g. results[[1]]), or just using the dollarsign notation "results$rt_plot"



### Making an analysis on each subject in a nested directory with a folder for each subject is easy you just give this function the path to where the subject folders are:

```{r message=FALSE, fig.show='hide', results='hide', warning=FALSE}
path_to_data = here("docs","source","examples","R","data")

out = here::here("..")

data = study_analysis(path = path_to_data, bayesian = FALSE, model = NA, folder = T, out = out)
```

#### These lines of code will then produce a results folder in each subject folder with the composite plot for the simple and if specified the bayesian analysis. Crucially individial's data is also stored, but also a combined file dataframe in csv format will appear in the working directory called "resulting_dataframe.csv". here the combined data is stored.

```{r}
read.csv(here("..","resulting_dataframe.csv")) %>% select(-X)%>% head(4)
```



