---
title: "Example_analysis_bayesian"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output: html_document
---


# **Here we show how to perform a bayesian analysis on the data after it has been collected which is very similar to the "simple" analysis. Please see the "simple analysis before this!**

```{r message=FALSE}
pacman::p_load(tidyverse,ggdist,psycho,caret,patchwork, gt, cowplot, grid,reticulate,cmdstanr,posterior,rstan,bayesplot,here,rmarkdown)
np <- import("numpy")
```


# **Reading in the data**
```{r message=FALSE}
#Here we read the same file as in the python notebook:
psychophysics_df = read_csv('https://github.com/embodied-computation-group/CardioceptionPaper/raw/main/data/Del2_merged.txt')
df = psychophysics_df %>% filter(Subject == "sub_0042")

```


```{r message=FALSE, results='hide',warning=FALSE}
#loading the functions to do the analysis:
source(here("docs","source","examples","R","src","firstlevelanalysis.R"))
```

The only difference here is that we set bayesian equal to T (TRUE) and specify the model. Here the model is a predefined Stan model that is inside the src folder called first_model.stan

**Doing the same as for the simple analysis with bayesian = T**

```{r message=FALSE, results='hide',warning=FALSE}
model = cmdstan_model(here("docs","source","examples","R","src","first_model.stan"))

results = single_sub_analysis(df, 
                              interoPost = NA, 
                              exteroPost = NA, 
                              bayesian = T, 
                              model = model, 
                              out = here::here("docs","source","examples","R"))
```

**The results list now also contains a new index called bayesian_plot. This is a list of either 1 or 3 plots. There'll be 1 if you only have one Morality and 3 if you have two (Extero and Intero). Here there is 3 plots**

Lets look at them individually:

```{r}
results$bayesian_plot[[1]]
```

**NOTE: The Import thing to look at for good model convergence is the upper plots: Here we see that all the 4 chains (to the left) seem to capture the same posterior distribution. It is also clear from the trace-plots to the upper right that the chains mix well (hairy catterpillars), meaning good convergence**

```{r}
results$bayesian_plot[[2]]
```


And the combined plot can be found in the last index
```{r, fig.height=8,fig.width=14}
results$bayesian_plot[[3]]
```


**Of cause this can be run through several subjects like the "simple" analysis**

```{r message=FALSE, fig.show='hide', results='hide', warning=FALSE}
path_to_data = here("docs","source","examples","R","data")

out = here::here("..")

data = study_analysis(path = path_to_data,
                      bayesian = T,
                      model = model,
                      folder = T,
                      out = out)
```



```{r}
read.csv(here("..","resulting_dataframe.csv")) %>% select(-X)%>% head(4)
```

### Here the Bayesian alpha is the threshold and the beta is the slope

